Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-11-12 journal/ms.Rmd
journal corrections

 Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages. We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies. The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.

@@

Besides these word-level properties, the lexical structure (that is, how words relate to each other) also influences the age of acquisition of words.  The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words (e.g., Collins and Loftus, 1975). Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological relatedness. These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].

While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process. In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind. According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99]. In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon.  In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment. They called this alternative explanation Preferential Acquisition. For clarity of reading, we will call preferential attachment the Internally-driven mechanism (INT), and preferential acquisition the Externally-driven mechanism (EXT). Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network. These two proposals represent two divergent ideas about the role of lexical networks in acquisition. On the INT proposal, network structure is a causal factor in early word learning; in contrast, on the EXT approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.

@@

@hills2009 found that early lexical networks do not grow through INT as was originally hypothesised by @steyvers2005, but rather through EXT. This finding, though potentially very profound, has only been established in the special case of networks that are based on 1) semantic associations,  2) production-based vocabularies, and 2) data from English-learning children, only. The extent to which this result depends on the domain, the measure and culture/language is still unclear. In this work, we test the generality of the finding along these three dimensions.

First, we study the phonological network in addition to the semantic network. These two networks represent different ways the mental lexicon is structured. In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa. Does the phonological network also influence word learning? Previous work did find an effect of words' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014]. In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life. However, this finding is compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.  Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
<!--
The phonological strcuture influence word processing in adults (Vitevitch, 2008;  Chan & Vitevitch, 2009; Chan & Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al. 2018). Here we test whether the mechanism of networtk growth in the phonological domains mirrors the mechanism found in the semantic domains. -->

@@

Finally, we use developmental data in 10 languages. Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010].\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.} Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the chidlren's learning strategy. Thus, Cross-linguistic comparison is crucial to test what mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014].

@@

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94]. When filling out a CDI form, caregivers are either invited to indicate whether their child "understands" (comprehension) or "understands and says" (production) each of about 400-700 words. For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried. We use data from younger children to test comprehension and data from older children to test production across 10 languages. Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns. Table \@ref(tab:stats) gives an overview of the data.

@@

kable(statistics, format = "latex", escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Statistics for data from Wordbank.",
      col.names = c("Language",  "Nouns", "Ages", "Nouns", "Ages")) %>%
  add_header_above(c("", "Comprehension" = 2, "Production" = 2)) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")

@@

Since  the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across languages. Using the same association data across languages does not necessarily mean that the resulting networks will be the same across languages, or that these networks will grow similarly. Indeed, though this approximation assumes that the semantic similarity measure is universal––which is a reasonable assumption (e.g., Youn et al. 2015), the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.

@@

The plots show, overall, a negative correlation between the month of acquisition and the degree.  In production data, the average correlation across languages was `r ps_ave` (SD=`r ps_sd`) for the semantic networks and `r pp_ave` (SD=`r pp_sd`) for the phonological networks.  In comprehension data, the average correlation was `r cs_ave` (SD=`r cs_sd`) for the semantic networks and `r cp_ave` (SD=`r cp_sd`) for the phonological networks. These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English (e.g., Storkel 2004, 2009; Hills et al. 2009) and extending these findings to ten different languages (with few exceptions) in both production- and comprehension-based vocabularies.

@@

We also analyzed the global network's degree distribution. The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution, i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$ [@barabasi99]. If the network displays this property, this fact would suggest an INT-like generative process. Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for INT. The log-log plots are shown in Figure \@ref(fig:degreeDist). We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using a related R package [poweRlaw, @gillespie15].

@@

Overall, we could not reject the null hypothesis of a power-law distribution: The $p$-value was generally above 0.1 in almost all languages for both production and comprehension. That said, phonological networks had relatively larger cut-offs than semantic networks. As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks ––as well as the observed cross-linguistic variability in the value of the cut-offs–– may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words. Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.

@@

First, the results replicate Hills et al.'s original finding regarding the semantic network in English and production data, which is that this network grows by EXT, not by INT. Second, our results show that, generally speaing, this finding generalizes to comprehension, and holds across languages. This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.} and phonological domains.

@@

Above we showed that the way semantic and phonological information is structured in the learning environment contributes to noun learning (via EXT) across languages. However, we know that other factors influence learning as well [e.g., @braginsky2016]. Next we investigated how semantic and phonological connectivity interact with two other factors. The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g. @goodman2008]. The second factor is word length, which was shown to correlate with phonological connectivity: Shorter words are more likely to have higher connectivity (Pisoni et al., 1985; Vitevitch and Rodriguez, 2004).

@@

For word length, we counted the number of phonemes in our generated IPA transcription. For word frequency, we used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language (MacWhinney, 2000). For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g. "father" counts as "daddy"). Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input (see Goodman et al. 2008).

@@

As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences. Connectivity contributes to learning in some languages but not in other. In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length. This contrasts with the original finding in @hills2009. However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates. Another important difference is the number of words tested: Our study uses a larger set of nouns. That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.

@@

This study provided an analysis of network growth during development. We compared two network growth scenarios described in the pioneering work of @steyvers2005 and @hills2009.  The first scenario, INT (originally called Preferential Attachment), described a rich-get-richer network growth model in which the current structure of the learner's internal network determines future growth; the other, EXT (originally called Preferential Acquisition) described a model in which the external, global environmental network structure determines learners' growth patterns. These two mechanisms represent two fundamentally different accounts of lexical growth: one suggests that future word knowledge is primarily shaped by the children’s past knowledge and its organization, whereas the other suggests that learning is shaped, rather, by salient properties in the input regardless of how past knowledge is organized.

Previous work [@hills2009; @hills2010] has been limited in its scope: It focused primarily on semantic networks, production-based vocabularies, and developmental data from English-learning children. The present study tested the generality of previous findings by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.

@@

These findings corroborate the hypothesis that children start by learning words that have high similarity to a variety of other words in the learning environment, not in the child's available lexicon. This means, strikingly, that children are sensitive to highly connected words although they do not initially have access to the full network. This finding raises some important questions. What mechanism allows children to distinguish highly connected words from other words? Besides, why would highly connected words be easier to learn?

One possibility is that children rely on their statistical learning abilities. For example, in the semantic domain, children might be using a mechanism akin to cross-situational learning to pick up the meanings of some words, especially concrete nouns [@smith2008], and such learning would resemble the growth scenario described by EXT.  Indeed, since free association is related to contextual co-occurrence (Griffiths et al., 2007), highly connected words will tend to occur in a variety of speech and referential contexts.  This fact makes such words easier to learnonly because they have more referential disambiguating cues across learning contexts, and crucially, even without knowing the entire set of words with witch they occurs (hence the similarity with EXT). This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].

In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking lwo level statistical patterns, e.g., high probability sound sequences. Indeed, connectivity in the phonological network is inherently correlated with phonotactic probability [@vitevitch1999]. That is, highly connected words tend to be made of frequent sound sequences. Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [e.g., @storkel2001]. This explanation is supported by computational simulations that shows how learning general phonotactics patterns create ``well-worn paths'' which allow the models to represent several distinct but phonologically neighboring words (Dell et al; 1993; Takac et al. 2017).

Besides using their own statistical learning skills, children could also benefit from the way their caregivers speak. Perhaps the caregivers put more emphasis on the words that are highly connected in _their_ mature lexical network. This emphasis would guide children to learn first these highly connected words even though children do not have access to the distribution of words' connectivity in the final network.  Investigating this possibility would require further research on caregiver-child interaction [@macwhinney2014; @roy2015], examining what words are introduced over development and the extent to which children's uptake is influenced by this input (Clark 2007;  Hoff and Naigles, 2002; Hurtado et al., 2008).

This work shares a number of limitations with previous studies using similar research strategy and datasets (e.g., Hills et al. 2009; 2010). Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional). Although this measure has proven highly consistent (Fensen et al. 1994), it lead us to focus on studying the learning mechanism of the "average" child. Individual trajectories, however, could show different learning patterns. For example, using longitudinal data @beckage2011 found differences between typical and late talkers in terms of the semantic network structure. Besides, although our study endorses the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage and Colunga, under review). For example, some children develop "islands of expertise", that is, well organized knowledge about a certain topic (e.g., birds or dinosaurs). This prior knowledge enables these children to learn new related words more easily (e.g., Chi and Koeske, 1983).

>>>>

 Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment, instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages. We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies, even controlling for word frequency and length. This pattern of findings suggests a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.

@@

Besides these word-level properties, the structure of the lexicon (that is, how words relate to each other) also predicts the age of acquisition of words.  The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words [e.g., @collins1975]. Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features, target-cue relationships in free association norms, co-occurrence in child directed speech, and phonological relatedness. These studies have found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].

While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process. In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind. According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99]. In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon.  In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment. They called this alternative explanation Preferential Acquisition. For clarity of reading, we will call preferential attachment the Internally-driven mechanism (INT), and preferential acquisition the Externally-driven mechanism (EXT). Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network.

These two proposals represent two divergent ideas about the role of lexical networks in acquisition. On the INT proposal, learning is driven by known words with high connectivity to other known words (Figure 1, left). Thus, the network structure is a causal factor in early word learning, that is, children might be relying on the organization of their past knowledge to determine future learning. For example, having a rich and organized knowledge about the domain of dinosaurs would facilitate the acquisition of new dinosaur-related words [@chi1983]. In contrast, on the EXT approach, learning is driven by the connectivity of words that are not known yet (Figure 1, right). Thus, the relevant network structure is not internally represented by children, and the related connectivity effect might be an epiphenomenon of some low level properties of the linguistic input. For example, highly connected words in the input could be more easily learned because of their contextual diversity [e.g., @smith2008] or because caregivers emphasize such words in child-directed speech [@macwhinney2014].

@@

@hills2009 investigated the growth of lexico-semantic networks in toddlers and found that growth did not proceed according to INT as was originally hypothesised by @steyvers2005, but rather according to EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known. However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is a profound finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized. However, this work has been done in the special case of networks that are based on 1) semantic associations, 2) production-based vocabularies, and 2) data from English-learning children, only. The extent to which this result depends on the domain (e.g., semantic vs. phonological connectivity), the vocabulary measure (production vs. comprehension) and culture/language is still unclear. In this work, we test the generality of the finding along these three dimensions.

First, we study the phonological network in addition to the semantic network. These two networks represent different ways the mental lexicon is structured. In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa. Does the phonological network also predict word learning? Previous work did find an effect of words' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014]. In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life. However, this finding is *a priori* compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.  Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
<!--
The phonological strcuture influence word processing in adults (Vitevitch, 2008;  Chan & Vitevitch, 2009; Chan & Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al. 2018). Here we test whether the mechanism of networtk growth in the phonological domains mirrors the mechanism found in the semantic domains. -->

@@

Finally, we use developmental data in 10 languages. Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010]. Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the children's learning strategy. Thus, Cross-linguistic comparison is crucial to test what mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014]. 
 <!--
\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.}
-->

We test the growth scenarios using parent reports of children vocabularies and their normative age of acquisition [@fenson94].  Children may vary in their individual learning trajectories, but the aggregate data leads to an average learning pattern which is highly consistent. It is this normative trajectory that we model in the current study, following the steps of previous research using similar datasets [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008; @braginsky2016]

@@

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94]. When filling out a CDI form, caregivers are either invited to indicate whether their child "understands" (comprehension) or "understands and says" (production) each of about 400-700 words. For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried. Thus, we use data from younger children to test comprehension and data from older children to test production across 10 languages. Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns. Table \@ref(tab:stats) gives an overview of the data.

@@

kable(statistics, format = "latex", escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Statistics for dataset we used.",
      col.names = c("Language",  "Nouns", "Ages", "Nouns", "Ages")) %>%
  add_header_above(c("", "Comprehension" = 2, "Production" = 2)) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")

@@

Since  the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across languages. Using the same association data across languages does not necessarily mean that the resulting networks will be the same across languages, or that these networks will grow similarly. Indeed, though this approximation assumes that the semantic similarity measure is universal––which is a reasonable assumption [e.g., @youn2016], the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.

@@

The plots show, overall, a negative correlation between the month of acquisition and the degree.  In production data, the average correlation across languages was `r ps_ave` (SD=`r ps_sd`) for the semantic networks and `r pp_ave` (SD=`r pp_sd`) for the phonological networks.  In comprehension data, the average correlation was `r cs_ave` (SD=`r cs_sd`) for the semantic networks and `r cp_ave` (SD=`r cp_sd`) for the phonological networks. These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English (e.g., Storkel 2004, 2009; Hills et al. 2009) and extending these findings to ten different languages, generally, in both production- and comprehension-based vocabularies.

@@

We also analyzed the global network's degree distribution. The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution, i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$ [@barabasi99]. If the network displays this property, this fact would suggest, but not prove, an INT-like generative process. If the degree distribution does not follow a power law, this  would largely weaken the case for INT. The log-log plots are shown in Figure \@ref(fig:degreeDist). We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using a related R package [poweRlaw, @gillespie15].

@@

Overall, we could not reject the null hypothesis of a power-law distribution: The $p$-value was generally above 0.1 in almost all languages for both production and comprehension. That said, phonological networks had relatively larger cut-offs than semantic networks. As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks–as well as the observed cross-linguistic variability in the value of the cut-offs–may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words. Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.

@@

First, the results replicate Hills et al.'s original finding regarding the semantic network in English and production data, which is that this network grows by EXT, not by INT. Second, our results show that, generally speaking, this finding generalizes to comprehension, and holds across languages. This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.} and phonological domains.

@@

Above we showed that the way semantic and phonological information is structured in the learning environment contributes to noun learning (via EXT) across languages. However, we know that other factors influence learning as well [e.g., @braginsky2016]. Next we investigated how semantic and phonological connectivity interact with two other factors. The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g. @goodman2008]. The second factor is word length, which was shown to correlate with phonological connectivity: Shorter words are more likely to have higher connectivity [@pisoni1985; @vitevitch2005].

@@

For word length, we counted the number of phonemes in our generated IPA transcription. For word frequency, we used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language [@macwhinney2014]. For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g. "father" counts as "daddy"). Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input [see @goodman2008].

@@

As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences. Connectivity contributes to learning in some languages but not in other. In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length. This contrasts with the original finding in @hills2009. However, this might be due to our using of a slightly different model (which included word length as a covariate) and a larger dataset. That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.

@@

This study provided an analysis of network growth during development. We compared two network growth scenarios described in the pioneering work of @steyvers2005 and @hills2009.  The first scenario, INT (originally called Preferential Attachment), described a rich-get-richer network growth model in which the current structure of the learner's internal network determines future growth; the other, EXT (originally called Preferential Acquisition) described a model in which the external, global environmental network structure determines learners' growth patterns. These two mechanisms represent two fundamentally different accounts of lexical growth: One suggests that future word knowledge is primarily shaped by the children’s past knowledge and its organization, whereas the other suggests that learning is shaped, rather, by salient properties in the input regardless of how past knowledge is organized. The present study tested the generality of previous findings [@hills2009; @hills2010] by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.

@@

These findings corroborate the hypothesis that children start by learning words that have high similarity to a variety of other words in the learning environment, not in the child's available lexicon. This hypothesis implies that children are sensitive to highly connected words although they do not initially have access to the full network, thus raising some important questions: What mechanism allows children to distinguish highly connected words from other words? Besides, why would highly connected words be easier to learn?

One possibility is that these patterns emerge from children’s use of statistical learning abilities [@saffran1996; @aslin2012; @smith2008]. The term "statistical learning" has been used in the developmental literature to describes the process by which one acquires information about their environment through tracking the frequency distribution of some elements (e.g., words) in different contexts. An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input. Previous work in the line of research has documented mechanisms which can explain the patterns found in the current study.

For example, in the semantic domain, growth according to EXT can be explained by a mechanism similar to cross-situational learning [@smith2008; @pinker2013; @yurovsky2015]. According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents. The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word "ball" is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows  the learner  to  narrow down the set of possible word-object mappings.  In our case, free association is related to contextual co-occurrence [@griffiths07], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.  This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts, and crucially, even without knowing the entire set of words with witch they co-occur (hence the similarity with EXT). This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].

In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking lwo level statistical patterns, e.g., high probability sound sequences. Indeed, connectivity in the phonological network is inherently correlated with phonotactic probability [@vitevitch1999]. That is, highly connected words tend to be made of frequent sound sequences. Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [@storkel2001]. This explanation is supported by computational simulations that shows how learning general phonotactics patterns create ``well-worn paths'' which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017].

Besides using their own statistical learning skills, children could also benefit from the way their caregivers speak. Perhaps the caregivers put more emphasis on the words that are highly connected in *their* mature lexical network. This emphasis would guide children to learn first these highly connected words even though children do not have access to the distribution of words' connectivity in the final network.  Investigating this possibility would require further research on caregiver-child interaction [@macwhinney2014; @roy2015], examining what words are introduced over development and the extent to which children's uptake is influenced by this input [@clark2007; @hoff2002].

This work shares a number of limitations with previous studies using similar research strategy and datasets. Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional). Although this measure has proven highly consistent [@fenson94], it led us to focus on studying the learning mechanism of the "average" child. Individual trajectories, however, could show different learning patterns. For example, using longitudinal data @beckage2011 found differences between typical and late talkers in terms of the semantic network structure. Besides, although our study endorses the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage and Colunga, under review). For example, some children develop "islands of expertise", that is, well organized knowledge about a certain topic (e.g., birds or dinosaurs). This prior knowledge enables these children to learn new related words more easily [e.g., @chi1983].
